Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-14 Ben_Manuscripts/structure_paper/Draft.tex
edits

\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
%\documentclass{article}
%jpcbfk

@@

  Nanostructured porous membranes made from the cross-linked hexagonal phase of
  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
  selective separations. In this work, we develop an atomistic molecular model
  of an experimentally characterized LLC membrane. While it is relatively 
  straightforward to create a stable hexagonal phase model, we demonstrate that 
  closely reproducing the experimental pore structure requires a carefully 
  constructed initial configuration in order to avoid falling into a metastable
  basin. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
  maximum consistency between our structures and experiment. We show that pores 
  are likely composed of 5 columns of stacked LLC monomers which surround each
  hydrophilic core. Although this system has been reported as dry, we show that
  small amounts of water are necessary to fully reproduce the experimental XRD
  pattern due to asymmetries introduced by hydrogen bonds between monomer head
  groups and water molecules. We explore, in depth, the composition and 
  structure of the nanopores and reveal that there exists a composition gradient
  rather than a hard partition between the hydrophilic and hydrophobic regions.
  The clearer picture of the nanoscopic structure of these membranes provided in
  this study will enable a better understanding of the mechanisms of small 
  molecule transport within these nanopores.

@@

  More highly selective membranes would be extremely useful for the recovery of valuable
  products from complex aqueous and organic solutions. For example, flowback
  water (FW) produced during hydraulic fracturing is a complex wastewater full of
  potentially valuable dissolved organic compounds such as acetate
  \cite{dischinger_application_2017}. There is increasing pressure to reuse
  hydraulic fracturing water rather than dispose of it in order to reduce social
  and environmental impacts as well as cost \cite{theodori_hydraulic_2014}.
  Rather fully than dispose of the wastestream generated in the recycling
  process, we can instead use highly selective membranes in order to successfully
  recover useful compounds.

@@

% MRS6: I would keep a paragraph about here how current membranes DON'T
% work for this purpose. But one paragraph is enough.
% BJC5: added back below paragraph.  
% MRS7: Do a pass for clarity at the sentence level.  For example ``degree of stochasticity'' is vague.
  Current commercial RO and NF membranes suffer limitations to their selectivity 
  which is inherent to their fabrication. Although scalable, each of these two types
  of membranes has a degree of stochasticity that makes overcoming well-known the 
  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
  the permeability of a desired molecular or atomic species, while maintaining the same 
  retention of an undesired species \cite{werber_materials_2016}.

@@

  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
  performing highly selective separations. LLCs are amphiphilic molecules that
  have the ability to self-assemble into porous nanostructures
  \cite{smith_ordered_1997} which can be crosslinked to create mechanically
  strong membrane films with pores on the order of 1 nm in diameter
  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
  are uniform in size because they are self-assembled. 
  Since LLC membranes lack a pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  described in this paper are salts, and therefore lead to Donnan exclusion of ions
  in solution. The membrane gains a net surface charge when counterions from the head
  groups that line the pore walls escape into the feed solution in order to balance 
  the gradients of concentration and electric potential \cite{donnan_theory_1995}.

  The feasibility of nanostructured LLC membranes for selective separations has been
  demonstrated using LLCs that form the type 1 bicontinuous cubic (Q\textsubscript{I})
  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
  phases (See Figure~\ref{fig:bcc_v_hII}). When separating organic solutes from
  NaCl, Q\textsubscript{I} phase membrane filtration experiments have shown
  selectivity 2--3 times higher than commercial RO and 6--12 times higher than
  commercial NF membranes \cite{dischinger_application_2017}.  When separating a
  series of various sized dyes, the H\textsubscript{II} phase membrane showed
  complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.

  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}). 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
  In 2016, Feng et al. showed that one could obtain the same result using a second
  technique termed soft confinement\cite{feng_thin_2016}. Current efforts are focused
  on extending the method to the H\textsubscript{II} phase and characterizing the 
  performance of these newly aligned systems.

@@

% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
% columns instead?
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

  Our current understanding of the molecular details of LLC membrane nanostructure
  is not sufficient to be able to precisely design them for specific separations. 
  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane studies have
  been limited primarily to Na-GA3C11 with some characterization done after minor 
  structural modifications. Resel et al.~varied the length of the monomer tails and the
  counterion used and observed its affect on pore spacing \cite{resel_structural_2000}.
  In a later study of rejection performance, it was shown that membranes formed by cross-
  linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes less than 1.2 
  nm in diameter because the pores are too large \cite{zhou_supported_2005}. We do not
  yet understand how to controllably reduce the effective pore size or how to tune
  the chemical environment in the nanopores of this or related materials for
  small molecule separations. The only source of predictive modeling for LLC
  systems have been macroscopic models that likely do not adequately describe
  transport at these length scales \cite{hatakeyama_water_2011}. 
  %MRS7: maybe a pass at this?
  Modeling with molecular detail could provide sufficient information about the mechanisms 
  and chemical features to better inform experimental design of similar nanostructured membranes. 
  %It will be
  %challenging to efficiently narrow down the large design space in a laboratory
  %setting without a robust model.

  %MRS7: changing future tense to present tense here.
  A molecular-level understanding of LLC polymer membrane structure, enabled by
  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which is crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations can provide the required level of detail
  (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
  With such an atomistic model, we can directly observe molecular-level solute
  transport and suggest governing mechanisms. We can observe how the choice of
  head group interacts with solutes of interest. We can interchange
  counterions which may influence both the pore size and the strength of the
  Donnan potential. 
  %which affects the degree to which the membrane can exclude
  %charged species at the membrane surface.

  In this study, we build a significantly more realistic atomistic model of LLC
  membranes than, to our knowledge, has ever previously been created, and explore
  what new structural information can be gained and what structure hypotheses are
  supported by this model. We validate the model using as much experimental
  information as possible. We are most interested in reproducing the conclusions
  about structure drawn from small angle X-ray scattering (SAXS)
  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
  conductivity measurements \cite{feng_thin_2016}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
	space periodic spacing of 7.4 \AA~. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

@@

	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
	relative intensity.  Accordingly, we name these reflection R-spots. The
	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
	respective quadrants. In many liquid crystal systems one can explain the spots
	as the tilt angle of the alkane chains with respect to the membrane
	plane\cite{govind_simple_2001}.

	\item \textit{R-pores}: The final feature corresponds to the spacing
	and symmetry of the d\textsubscript{100} plane. This plane is geometrically
	related the distance between pores. The feature, which we named R-pores, is
	characterized by dots along the equatorial axis defined when $q_z$ = 0. The
	spacing between dots is indicative of the hexagonal symmetry of the packed
	pores. We observe the same information with higher resolution using SAXS
	(Fig.~\ref{fig:SAXS}).

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
        %MRS7: picture says R-helix still.
	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

	The limited picture that experiment provides tells us that there are hexagonally packed, 
	hydrophilic regions where transport is likely to occur. One may instinctively imagine these 
	regions as tube-like pathways with well-defined boundaries. We will explore the composition
	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
	sensitivity to initial configuration.

@@

	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
	ambient water may be leached into the system. The hydrogen bonding network formed by the 
	water may play a role in structuring the pore. We used simulated X-ray diffraction patterns
	to see if there is any meaningful structural difference between a "dry" and "wet" system.

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:python}a). See section S-\ref{S-section:parameterization} 
  for further detail.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (See section S~\ref{S-section:self_assembly}). 
  %BJC5: section showing self-assembly set up to be added
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended
  periodically. Each pore is made of columns of stacked monomers with periodic
  continuity along the pore axis, avoiding any edge effects and creating an
  infinite length pore ideal for studying transport. We prefer a small number stacked
  monomers in order to reduce computational cost and to allow us to look at
  longer timescales. Ultimately, we chose to build a system with 20 monomers
  per column in order to obtain sufficient resolution when simulating
  X-ray diffraction patterns. %This point will be explained in more detail later.
  %MRS7: refer to supporting information (if it's there) for more discussion on stability as a function of height?

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. The starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one choses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. The initial distance between pores, within a wide range, also has 
  little effect on the the equilibrated structure. However, one should not start them
  too close or there will be high energy repulsions during early equilibration. We 
  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
  Supporting information, section S-\ref{S-section:initial_config_dependence}. The 
  distance between vertically stacked monomers, the position of monomers with respect 
  to vertically adjacent monomers, and the number of columns per pore do influence the 
  equilibrated structure and require further justification for their choices. We rely on 
  experimental data to inform them.

  We chose the vertical spacing between monomers for the initial configuration based
  on R-$\pi$ and then allowed the system to readjust during equilibration. Each monomer was
  rotated so the plane of its aromatic head groups would be coplanar with the xy plane. We
  explored three different initial monomer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial spacing of 5
  \AA. We briefly explored a third system with an initial spacing of 10
  \AA. However this spacing yields non-physical behavior which is detailed in the 
  Supporting Information, section S-\ref{S-section:initial_dbwl}.

@@

  The number of columns per pore is unknown, as stated in question
  (\ref{point:monomernum}). We tested configurations constructed with a varied
  number of columns per pore. We built systems in the offset and parallel
  displaced configurations with 4, 5, 6, 7 and 8 monomers per layer.

>>>>

\documentclass[journal=jpcbfk,manuscript=article]{achemso}

@@

  Nanostructured porous membranes made from the cross-linked hexagonal phase of
  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
  selective separations. In this work, we develop an atomistic molecular model
  of an experimentally characterized LLC membrane. While it is relatively 
  straightforward to create a stable hexagonal phase model, we demonstrate that 
  closely reproducing the experimental pore structure requires a carefully 
  constructed initial configuration in order to avoid falling into metastable
  basins. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
  maximum consistency between our structures and experiment. We show that pores 
  are likely composed of 5 columns of stacked LLC monomers which surround each
  hydrophilic core. Although this system has been reported as dry, we show that
  small amounts of water are necessary to fully reproduce the experimental XRD
  pattern due to asymmetries introduced by hydrogen bonds between monomer head
  groups and water molecules. We explore the composition and structure of the 
  nanopores and reveal that there exists a composition gradient rather than a 
  hard partition between the hydrophilic and hydrophobic regions. The clearer 
  picture of the nanoscopic structure of these membranes provided in
  this study will enable a better understanding of the mechanisms of small 
  molecule transport within these nanopores.

@@

  More highly selective membranes would be extremely useful for the recovery of 
  dissolved species in complex aqueous and organic solutions. For example, selective
  membranes can further progress forward osmosis processes by reducing the cost of 
  separating potable water from draw solutions~\cite{mccutcheon_novel_2005}. Additionally, 
  flowback water (FW) produced during hydraulic fracturing is a complex wastewater full
  of potentially valuable dissolved organic compounds such as acetate 
  that can be recovered using highly selective membranes \cite{dischinger_application_2017}.
  Finally, a significant amount of nitrogen and phosphorus from fertilizer is found in 
  wastewater. Selective membranes offer a route towards low energy nutrient recovery 
  from these wastewaters which can help sustain fertilizer production and subsequently
  food production into the future \cite{xie_membrane-based_2016}.
  % as we near peak production of minable phosphorus rock .

%  There is increasing pressure to reuse
%  hydraulic fracturing water rather than dispose of it in order to reduce social
%  and environmental impacts as well as cost \cite{theodori_hydraulic_2014}.
%  Rather fully than dispose of the wastestream generated in the recycling
%  process, we can instead use highly selective membranes in order to successfully
%  recover useful compounds.

@@

% MRS6: I would keep a paragraph about here how current membranes DON'T
% work for this purpose. But one paragraph is enough.
% BJC5: added back below paragraph.  
% MRS7: Do a pass for clarity at the sentence level.  For example ``degree of stochasticity'' is vague.
  Current commercial RO and NF membranes suffer limitations to their selectivity
  because they are unstructured. Although scalable, their fabrication involves the 
  spontaneous assembly of polymers into disordered structures which offer separation 
  pathways that are tortuous and polydisperse in size. This makes overcoming the well-known 
  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
  the permeability of a desired molecular or atomic species, while maintaining the 
  same retention of an undesired species \cite{werber_materials_2016}.

@@

  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
  performing highly selective separations. LLCs are amphiphilic molecules that
  have the ability to self-assemble into porous nanostructures
  \cite{smith_ordered_1997} and can be crosslinked to create mechanically
  strong membrane films with pores on the order of 1 nm in diameter
  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
  are uniform in size because they are self-assembled. 
  Since LLC membranes lack a pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  described in this paper are salts, and therefore lead to Donnan exclusion of ions
  in solution. The membrane gains a net surface charge when counterions from the head
  groups that line the pore walls escape into the feed solution in an effort to balance 
  the gradients of concentration and electric potential \cite{donnan_theory_1995}.

  The feasibility of nanostructured LLC membranes for selective separations has been
  demonstrated using LLCs that form the type 1 bicontinuous cubic (Q\textsubscript{I})
  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
  phases. When 
  separating organic solutes from NaCl, Q\textsubscript{I} phase membrane filtration
  experiments have shown selectivity 2--3 times higher than commercial RO and
  6--12 times higher than commercial NF membranes \cite{dischinger_application_2017}.
  When separating a series of various sized dyes, the H\textsubscript{II} phase membrane
  showed complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.

  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014}. 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
  In 2016, Feng et al. showed that one could obtain the same result using a second
  technique termed soft confinement\cite{feng_thin_2016}. Current experimental 
  efforts are focused on extending the method to the H\textsubscript{II} phase 
  and characterizing the performance of these newly aligned systems.

@@

% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
% columns instead?
% BJC6 : I will get to redo-ing this. Just takes some time to refamiliarize myself with
% the software I used to create it
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

  Our current understanding of the molecular details of LLC membranes' nanostructure
  is not sufficient to be able to precisely design them for specific separations. 
  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane studies have
  been limited primarily to Na-GA3C11 with some characterization done after minor 
  structural modifications. Resel et al.~varied the length of the monomer tails and the
  counterion used and observed its effect on pore spacing \cite{resel_structural_2000}.
  In a later study of rejection performance, it was shown that membranes formed by cross-
  linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes less than 1.2 
  nm in diameter because the pores are too large \cite{zhou_supported_2005}. We do not
  yet understand how to controllably reduce the effective pore size or how to tune
  the chemical environment in the nanopores of this or related materials for
  small molecule separations. The only source of predictive modeling for LLC
  systems have been macroscopic models that likely do not adequately describe
  transport at these length scales \cite{hatakeyama_water_2011}. Modeling with molecular
  detail could provide sufficient information about the mechanisms and chemical features
  to better inform experimental design of similar nanostructured membranes.

  A molecular-level understanding of LLC membrane structure, enabled by
  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which is crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations can provide the required level of detail
  (Figure \ref{fig:detail}), assuming the force fields are sufficiently accurate.
  With such an atomistic model, we can directly observe molecular-level solute
  transport and suggest governing mechanisms. We can observe how the choice of
  head group interacts with solutes of interest. We can interchange
  counterions which may influence both the pore size and the strength of the
  Donnan potential. 
  %which affects the degree to which the membrane can exclude
  %charged species at the membrane surface.

  %BJC6: is this too bold considering the work done at University of Wisconsin?
  In this study, we build a significantly more realistic atomistic model of LLC
  membranes than, to our knowledge, has ever previously been created, and explore
  what new structural information can be gained and what structure hypotheses are
  supported by this model. We validate the model using as much experimental
  information as possible. We are most interested in reproducing the conclusions
  about structure drawn from small angle X-ray scattering (SAXS)
  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
  conductivity measurements \cite{feng_thin_2016}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
	space periodic spacing of 7.4 \AA~. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

@@

	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
	relative intensity.  Accordingly, we name these reflection R-spots. The
	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
	respective quadrants. In many liquid crystal systems one can explain the spots
	as the product of alkane chains tilted with respect to the membrane
	plane\cite{govind_simple_2001}.

	\item \textit{R-pores}: The final feature corresponds to the spacing
	and symmetry of the d\textsubscript{100} plane. This plane is geometrically
	related the distance between pores. The feature, which we named R-pores, is
	characterized by dots along the equatorial axis defined by $q_z$ = 0. The
	spacing between dots is indicative of the hexagonal symmetry of the packed
	pores. We observe the same information with higher resolution using SAXS
	(Fig.~\ref{fig:SAXS}).

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

	The limited picture that experiment provides tells us that there are hexagonally packed, 
	hydrophilic regions where transport is likely to occur. One may instinctively imagine these 
	regions as tube-like pathways with well-defined boundaries. We explored the composition
	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
	sensitivity to initial configuration.

@@

	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
	ambient water may be leached into the system. The hydrogen bonding network formed by the 
	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
	to see if there is any meaningful structural difference between a "dry" and "wet" system.

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:python}a). See section S\ref{S-section:parameterization} 
  for further detail.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (See section S\ref{S-section:self_assembly}). 
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended
  periodically. Each pore is made of columns of stacked monomers with periodic
  continuity along the pore axis, avoiding any edge effects and creating an
  infinite length pore ideal for studying transport. We prefer a small number of stacked
  monomers in order to reduce computational cost and to allow us to look at
  longer timescales. Ultimately, we chose to build a system with 20 monomers
  per column in order to obtain sufficient resolution when simulating
  X-ray diffraction patterns (see further discussion in section S\ref{S-section:monomers_per_column}).
  %MRS7: refer to supporting information (if it's there) for more discussion on stability as a function of height?
  %BJC6: gave it a shot in supplemental

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. The starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one choses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. The initial distance between pores, within a wide range, also has 
  little effect on the the equilibrated structure. However, one should not start them
  too close or there will be high energy repulsions during early equilibration. We 
  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
  Supporting information, section S\ref{S-section:initial_config_dependence}. The 
  distance between vertically stacked monomers, the position of monomers with respect 
  to vertically adjacent monomers, and the number of columns per pore do influence the 
  equilibrated structure and require further justification for their choices. We rely on 
  experimental data to inform them.

  We chose the vertical spacing between monomers for the initial configuration based
  on R-$\pi$ and then allowed the system to readjust during equilibration. Each monomer was
  rotated so the plane of its aromatic head group would be coplanar with the xy plane. We
  explored three different initial monomer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial spacing of 5
  \AA. We briefly explored a third system with an initial spacing of 10
  \AA. However this spacing yields non-physical behavior which is detailed in the 
  Supporting Information, section S\ref{S-section:initial_dbwl}.

@@

  The number of columns per pore is unknown, as stated in question
  (\ref{point:monomernum}). We tested configurations constructed with a varied
  number of columns per pore. We built systems in the sandwiched and parallel
  displaced configurations with 4, 5, 6, 7 and 8 monomers per layer.
